### 2016-06-13 LITES/response.tex

\action{Section 2 was rewritten and expanded to clearly distinguish between the runtime rule (Section 2.2) and the classic analysis (Section 2.3). The runtime rule --- Equation (1) --- is stated in terms of multi-segmented deferrable tasks. }

\action{Section 4 was completely rewritten to more clearly explain that the problem of finding a suitable corresponding task set is open, and likely difficult.}

	\item 
Section 4 should be reworded. 'precisely converting a self-suspending task
system into a corresponding single-segment deferrable task set is not an
easy problem'  $\rightarrow$  'converting a self-suspending tasks system into a
single-segment deferrable task set introduced pessimism due to period
enforcement'.

\begin{response}
We do not fully understand this recommendation. In any case, we have
completely rewritten this section; we hope that the current revision addresses this concern as well.
\end{response}

@@

%There is no additional pessimism due to the period enforcer algorithm. The pessimism is due to the assumption made by the period enforcer algorithm to allow only a set of deferrable tasks (that only suspend once at beginning). 	
\end{response}

\action{In the revision, we completely rewrote Section 4 to explain the gap between the segmented self-suspending task model and the corresponding deferrable sporadic task set, and to precisely state the equivalence of the conversion to the worst-case response-time analysis of individual computation segments (i.e., Nelissen et al.'s analysis).
}

	\item 
Section 5 should also include the scenario where period enforcement is only
applicable to the normal execution segments. It seems practical to not
enforce critical sections since they are usually short in most systems i.e.
the back-to-back execution overhead from most critical sections in
real-world scenarios should be minimal. The case 3 that should be discussed
is period enforcement applied to execution segment after the critical
section, without enforcing the critical section and just including its
back-to-back execution penalty in the worst-case analysis.

\begin{response}
Thank you for the suggestion; this is indeed an interesting option to explore. However, we believe a comprehensive exploration of all possible interpretations to be out of the scope of this paper.

@@

\begin{quote}
	``The scheduling penalty of deferred execution [when using synchronization protocols] can be enormous to the extent that it can make such protocols almost useless in several cases. \emph{The development of the period enforcer algorithm was primarily motivated by the need to reduce or eliminate this penalty} with a small, if not negligible, overhead. If tasks using these synchronization protocols use the period enforcer, their worst-case blocking durations would be considerably smaller and the schedulable utilization correspondingly higher.'' [26, Section 5.1]
\end{quote}

Our intention here is to document that this simply does not work. We do not claim to evaluate all possible ways in which the period enforcer might be used otherwise.

\end{response}

\action{We have added Section 5.4 to briefly comment on this third possible interpretation. We now also comment on distributed semaphore protocols (e.g., DPCP, DFLP). Illustrative examples are provided in Figures~7 and~8.}

### 2016-06-13 locking.tex
spell out DPCP and DFLP on first use

The examples in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} assume a \emph{shared-memory} locking protocol: once a lock is granted, tasks execute their own critical sections, on their assigned processors. One may wonder whether  effects similar to those described in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} can also occur under \emph{distributed} real-time locking protocols such as the DPCP~\cite{RSL:88} or the DFLP~\cite{Br:13,Br:14}, where critical sections may be executed on dedicated \emph{synchronization processors}. In this case, the self-suspension occurs on the task's \emph{application processor}, which is different from the (remote) synchronization processor on which the critical section is executed.

>>>>

The examples in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} assume a \emph{shared-memory} locking protocol: once a lock is granted, tasks execute their own critical sections, on their assigned processors. One may wonder whether  effects similar to those described in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} can also occur under \emph{distributed} real-time locking protocols such as the \emph{Distributed Priority Ceiling Protocol} (DPCP)~\cite{RSL:88,Raj:91} or the \emph{Distributed FIFO Locking Protocol} (DFLP)~\cite{Br:13,Br:14}, where critical sections may be executed on dedicated \emph{synchronization processors}. In this case, the self-suspension occurs on the task's \emph{application processor}, which is different from the (remote) synchronization processor on which the critical section is executed.
